Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-12-17 src/tf-cutcell-comparison/responses2.tex
move points down as well as up

Sections 4a and 4b – Section 4a presents results for the Sch\"{a}r advection test case for various vertical coordinates and advection schemes; there is little new here that is not already covered in the \citet{schaer2002} paper. The advection tests in section 4b provide an interesting counter example to this test. I would recommend switching the emphasis in these two sections, presenting the advected tracer contours in a new Fig. 3 for the terrain-following advection, and just including results from the Sch\"{a}r case in table 1 for comparison purposes.
\end{quotation}
\begin{quotation}
 Lines 131-147 on cut-cell grid generation - It's still not clear how or why a cell vertex  is moved laterally in constructing the cut-cell mesh. Taking Fig. 2 as an example, it  seems that following the authors' directions to move all vertices lying underneath the  orography on the uniform grid up to the surface would produce four grid cells as  shown in the figure below rather than the three cells shown in Fig. 2. This four-cell structure appears to be consistent with the generation of thin cells as the authors  point out in Fig. 5c. If lateral displacement of a vertex is allowed, how is it decided  whether it should be moved and how is it decided where along the surface it should  be located (i.e. the location of point v in Fig. 2)?
\end{quotation}
\TODO{redo everything using slanted cell grids}

>>>>

Sections 4a and 4b – Section 4a presents results for the Sch\"{a}r advection test case for various vertical coordinates and advection schemes; there is little new here that is not already covered in the \citet{schaer2002} paper. The advection tests in section 4b provide an interesting counter example to this test. I would recommend switching the emphasis in these two sections, presenting the advected tracer contours in a new Fig. 3 for the terrain-following advection, and just including results from the Sch\"{a}r case in table 1 for comparison purposes.
\end{quotation}
\begin{quotation}
 Lines 131-147 on cut-cell grid generation - It's still not clear how or why a cell vertex  is moved laterally in constructing the cut-cell mesh. Taking Fig. 2 as an example, it  seems that following the authors' directions to move all vertices lying underneath the  orography on the uniform grid up to the surface would produce four grid cells as  shown in the figure below rather than the three cells shown in Fig. 2. This four-cell structure appears to be consistent with the generation of thin cells as the authors  point out in Fig. 5c. If lateral displacement of a vertex is allowed, how is it decided  whether it should be moved and how is it decided where along the surface it should  be located (i.e. the location of point v in Fig. 2)?
\end{quotation}
We have found an alternative method of generating meshes that does not require the use of the \texttt{snappyHexMesh} utility.  This new method does not move vertices laterally and is more straightforward to describe.  This new method creates meshes that retain the long, thin cells from the old method.  The new method is described in section 2 and figure 2.  All test results on cut cell grids have been updated.

### 2015-12-17 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
move points down as well as up

Cut cell grids are generated in a different way to the typical shaving technique described by \citet{adcroft1997}.  Starting from a uniform grid, all cell vertices that lie beneath the orography are moved up to the surface.  Where all four of a cell's vertices are moved, the cell has zero volume and so it is removed.  Where two vertices at the same horizontal location are moved up to the surface they will occupy the same point; this results in a zero-length edge that is removed to create a triangular cell.  Figure~\ref{fig:grid-generation} shows how a $2 \times 2$-cell, uniform grid is transformed into a cut cell grid.  Cell $c_4$ is removed because it has zero volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.

>>>>

Cut cell grids are generated in a different way to the typical shaving technique described by \citet{adcroft1997}.  Starting from a uniform grid, all cell vertices that lie beneath the orography are moved up to the surface.  Additionally, to avoid creating very thin cells, all vertices up to $\Delta z/5$ above the orography are moved down to the surface.  \TODO{should I include an illustration of how this extra tweak helps?  can I incorporate it into the existing figure?} Where all four of a cell's vertices are moved, the cell has zero volume and so it is removed.  Where two vertices at the same horizontal location are moved up to the surface they will occupy the same point; this results in a zero-length edge that is removed to create a triangular cell.  Figure~\ref{fig:grid-generation} shows how a $2 \times 2$-cell, uniform grid is transformed into a cut cell grid.  Cell $c_4$ is removed because it has zero volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.
